Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2015-04-22 experiments.tex
fixed caption
corretti i due typo notificati

\section{A Case Study: VLIW Hardware/Software Design Space}
\secL{ee}
Although PS has been formally introduced and described as a general
multi-objective optimization algorithm, in this work we will
explicitly refer to the more restricted (but still very large)
embedded system design scenario,  since its properties
are the ones that suggested to the authors the concepts of Pareto-based
innovation and region scoring system.

@@

Low budget Pareto sets are shown in \figR{pareto_fronts_100}. Note
that with such a small number of configurations being investigated, the
two sets are often overlapping, being also strongly dependent upon the
application being considered.  These results are obtained in about 5
eras and demonstrate that, with such a limited budget, PS can compete with
genetic approach while even discovering very different Pareto fronts.
Considering the extended simulation budget as depicted in
\figR{pareto_fronts_500}, we can qualitatively observe that even if PS
does not strictly outperforms GA in terms of dominance, it shows
in some cases larger Pareto in terms of extension. We can intuitively
relate this to the ``novelty-based'' score system, so that instead of
focusing on getting better points inside a given range PS tries to
enlarge the range itself, resulting in less dense but more extended
Paretos. Of course we cannot classify this different behavior as
being strictly better or worse when compared to the genetic one: other
design factors should be evaluated on a case-by-case basis, e.g. the
desired granularity of the results, objective range constraints or
estimated error of the adopted models.

@@

\begin{figure}
  \figLC{dispersion}{(a)(b) Variation range obtained by PS and GA for
  different benchmarks and average dispersion absolute dispersion (c). }
  \begin{center}
    \subfigure[]{\includegraphics[width=0.7\textwidth]{pictures/variation_power.eps} }
    \subfigure[]{\includegraphics[width=0.7\textwidth]{pictures/variation_etime.eps} }
    \subfigure[]{\includegraphics[width=0.7\textwidth]{pictures/dispersion.eps} }
  \end{center}
\end{figure}

>>>>

\section{A Case Study: VLIW Hardware/Software Design Space}
\secL{ee}
Although PS has been formally introduced and described as a general
multi-objective optimization algorithm, in this work we will
embedded system design scenario,  since its properties
are the ones that suggested to the authors the concepts of Pareto-based
innovation and region scoring system.

@@

Low budget Pareto sets are shown in \figR{pareto_fronts_100}. Note
that with such a small number of configurations being investigated, the
two sets are often overlapping, being also strongly dependent upon the
application being considered.  These results are obtained in about 5
eras and demonstrate that, with such a limited budget, PS can compete with
genetic approach while even discovering very different Pareto fronts.
Considering the extended simulation budget as depicted in
\figR{pareto_fronts_500}, we can qualitatively observe that even if PS
does not strictly outperforms GA in terms of dominance, it shows
in some cases Pareto fronts whose extension is larger. We can intuitively
relate this to the ``novelty-based'' score system, so that instead of
focusing on getting better points inside a given range PS tries to
enlarge the range itself, resulting in less dense but more extended
Pareto fronts. Of course we cannot classify this different behavior as
being strictly better or worse when compared to the genetic one: other
design factors should be evaluated on a case-by-case basis, e.g. the
desired granularity of the results, objective range constraints or
estimated error of the adopted models.

@@

\begin{figure}
  \figLC{dispersion}{(a)(b) Variation range obtained by PS and GA for
  different benchmarks and average absolute dispersion errors (c). }
  \begin{center}
    \subfigure[]{\includegraphics[width=0.7\textwidth]{pictures/variation_power.eps} }
    \subfigure[]{\includegraphics[width=0.7\textwidth]{pictures/variation_etime.eps} }
    \subfigure[]{\includegraphics[width=0.7\textwidth]{pictures/dispersion.eps} }
  \end{center}
\end{figure}
